---
title: "Research in Progress"
css: [styles.css, inprogress_styles.css]
---

```{r}
#| include: false
#| echo: false

source("0_packages.R")

make_progress_tracker <- function(current_level = "B") {
  levels <- c("A", "B", "C", "D", "E")
  labels <- c(
    A = "Formal analysis plan",
    B = "Execute analysis",
    C = "Draft manuscript",
    D = "Submit to journal",
    E = "Manuscript accepted"
  )

  current_idx <- match(current_level, levels)
  n <- length(levels)
  fill_left  <- sprintf("%.4f%%", 100 / (2 * n))
  fill_width <- sprintf("%.4f%%", (current_idx - 1) / n * 100)

  stage_divs <- purrr::imap_chr(levels, \(lvl, i) {
    if (i < current_idx) {
      status <- "done"; icon <- "&#10003;"
    } else if (i == current_idx) {
      status <- "current"; icon <- as.character(i)
    } else {
      status <- "pending"; icon <- as.character(i)
    }
    paste0(
      '<div class="rr-pipeline-stage ', status, '">',
        '<div class="rr-stage-node">', icon, '</div>',
        '<div class="rr-stage-label">', labels[[lvl]], '</div>',
      '</div>'
    )
  })

  paste0(
    '<div class="rr-pipeline">',
      '<div class="rr-pipeline-stages">',
        '<div class="rr-pipeline-fill" style="left:', fill_left, '; width:', fill_width, ';"></div>',
        paste(stage_divs, collapse = "\n"),
      '</div>',
    '</div>'
  )
}

```

Below you will find brief descriptions of research projects that are in progress. For each entry, you will find a title, synopsis, status, and links to any additional information available for that project. Please note, we only list projects that the Research Ring is leading or majorly contributing to. We do not track projects team members collaborate on with other groups.

------------------------------------------------------------------------

### "Leading Causes of Death Among U.S. Firefighters" {#proj-ff-mortality}

------------------------------------------------------------------------

#### Synopsis:

Firefighting carries well-documented occupational hazards, but population-wide evidence on what firefighters actually die from remains thin. This project uses the National Occupational Mortality Surveillance (NOMS) data to examine cause-specific mortality among U.S. career firefighters from 2020 to 2024, comparing their mortality profile to the working-age U.S. population and to the patterns the Research Ring has already documented for [law enforcement officers](public_output.html#pub-2025-leo-mortality) and [correctional officers](public_output.html#pub-2026-correctional-officer-mortality). The analysis applies the same population-based approach used in those earlier studies, with a supplementary analysis that adds EMS personnel. Preliminary findings were [presented to the Tri-State FACE Team](public_media.html#uc-face-2026) in Cincinnati in September 2026; a manuscript is in preparation.

#### Status:

```{r results='asis'}
#| echo: false
cat(make_progress_tracker(current_level = "C"))
```

------------------------------------------------------------------------

### "Training Officers to Give Better LCAN Reports"

------------------------------------------------------------------------

#### Synopsis:

LCAN (Location, Conditions, Actions, Needs) is the brief radio report officers give command on arrival at an active attack. After-action reviews of major incidents repeatedly cite breakdowns in this kind of communication. LCAN is taught in ALERRT courses, but how well that training works has never been tested. This program of three studies will test it in steps. The first is an online study with university students, the second moves into virtual reality, and the third works with officers. Each study measures how complete participants' spoken reports are. The first study is expected to begin data collection in spring 2027.

#### Status:

```{r results='asis'}
#| echo: false
cat(make_progress_tracker(current_level = "A"))
```

------------------------------------------------------------------------

### "Deaths of Despair among Protective Service Occupations"

------------------------------------------------------------------------

#### Synopsis:

This project will assess the burden of deaths of despair across major protective service occupations (e.g., police, corrections, fire, EMS/paramedics) using large-scale administrative data.

#### Status:

```{r results='asis'}
#| echo: false
cat(make_progress_tracker(current_level = "B"))
```

------------------------------------------------------------------------

### "Moving Targets: Classification Drift and the Changing Profile of Active Shooter Events in the United States"

------------------------------------------------------------------------

#### Synopsis:

This project will examine longitudinal trends in active shooter incident resolutions using FBI data spanning 2000–2024, with a particular focus on whether the proportion of incidents ending with the attacker fleeing the scene has increased over time. Findings from this project will have direct implications for law enforcement training and operational preparedness, particularly as a growing share of active shooter responses may involve scene stabilization and suspect search operations rather than direct engagement.

#### Status:

```{r results='asis'}
#| echo: false
cat(make_progress_tracker(current_level = "D"))
```

------------------------------------------------------------------------

### "Examining Stress Habituation Across Repeated VR Scenario Exposures" 

------------------------------------------------------------------------

#### Synopsis:

This project will examine the effects of repeated exposure to stressful virtual reality (VR) scenarios on acute physiological stress responses, with the aim of evaluating whether habituation occurs across multiple exposures. Participants will complete three separate scenario days using a VR system, with salivary biomarkers collected at each session to index acute stress reactivity. This study is being conducted in collaboration with the MAP Lab at Texas State University.

#### Status:

```{r results='asis'}
#| echo: false
cat(make_progress_tracker(current_level = "B"))
```

------------------------------------------------------------------------

### "Calibration & validation of a police UoF assessment instrument" 

------------------------------------------------------------------------

#### Synopsis:
This project draws on data from the final evaluations of a defensive tactics class involving over 2,000 Brazilian police recruits. The evaluation used a standard reality-based simulation of a domestic call and an instrument designed to assess police performance in use-of-force incidents. This study now explores, validates, and calibrates that instrument.

#### Status:

```{r results='asis'}
#| echo: false
cat(make_progress_tracker(current_level = "B"))
```

------------------------------------------------------------------------

### "What officers should be trained for? (Brazil)" 

------------------------------------------------------------------------

#### Synopsis:

This project is a collaboration between U.S.-based scholars and Brazilian pracademics. It uses a mixed-methods approach, combining a national-level survey with over 20,000 responses, data from police reports from a Brazilian police department, and a focus group. Together, these sources are used to identify the use-of-force situations most commonly experienced by officers, the contextual factors that increase risk in those incidents, and other critical situations—all with the goal of informing police use-of-force training. Results will be compared with an ongoing parallel study being conducted with U.S. law enforcement.

#### Status:

```{r results='asis'}
#| echo: false
cat(make_progress_tracker(current_level = "C"))
```

